Development and Implementation of an ANN based flow law for Numerical Simulations of Thermo-mechanical Processes at High Temperatures in FEM Software

### 2023-01-10 Article.tex
Update Latex for revised paper

As we have seen in the previous paragraph, the choice of the flow law to use is generally guided mainly by the list of flow laws available in the Finite Element code used, and very often this choice is made at the expense of the quality of the model.
For example, Zhou \eal \cite{Zhou-2020}, proposed the identification of the flow law of a GCr15 alloy for a continuous casting bloom with heavy reduction application as introduced by Ji \eal \cite{Ji-2018} who have performed compression tests on this material.
In their study, Ji \eal \cite{Ji-2018} performed compression tests on GCr15 cylinders in a temperature range of $750~\celsius$ to $1300~\celsius$ in $50~\celsius$ steps, strain rates of $0.001~\ps$,  $0.01~\ps$ and $0.1~\ps$ and strains up-to $0.7$.
The results of these compression tests, plotted in Figure \ref{fig:Zhou-OriginalData}, show a decrease in flow stress $\sigma^y$ with respect to an increase of the temperature $T$ and a increase of $\sigma^y$ with respect to an increase of the strain rate $\mdot\varepsilon$, as in most metallic materials.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/Zhou-OriginalData}
\caption{Original Data.}
\label{fig:Zhou-OriginalData}
\end{figure}
The evolution of the flow stress as a function of the plastic deformation shows the presence of a dynamic recrystallization (DRX) phenomenon within the material.
This phenomenon is an additional non-linearity of this type of material compared to other materials, mainly due to high temperatures and low strain rates, which should be taken into account when describing the material behavior.
As stated in the publication of Zhou \eal \cite{Zhou-2020}, depending on the flow model used: Johnson-Cook, Modified Zerilli-Armstrong, Arrhenius or new Modified Johnson-Cook, the fidelity of taking into account the real behavior varies widely with the complexity of the flow model which includes between $5$ parameters for the Johnson-Cook model, and $16$ parameters for the Arrhenius model.
Thus, and for the input data provides by Ji \eal \cite{Ji-2018}, the two most common models: Johnson-Cook and Zerilli-Armstrong do not correctly describe the material behavior.
Only the modified Johnson-Cook and Arrhenius models are able to describe correctly the behavior of the material during the compression process.
Unfortunately, and this is not part of their study, if these last two models are satisfactory from a theoretical point of view, from a practical point of view for the user of a FE code such as Abaqus, it will be necessary to carry out a numerical implementation in a FORTRAN 77 VUMAT subroutine of the modified Johnson-Cook flow law or the Arrhenius law as carried out by few authors \cite{Liang-2022, Gao-2007-FRT, Ming-2018} in order to be able to use these laws for numerical simulation.
This requires a certain expertise in the development and implementation of flow laws, which is not available to all users of the Abaqus FE code.

From this observation, and from the necessity to select a flow law for a given type of material, then to identify the parameters of this flow law according to experimental tests, and finally to implement this flow law in the form of a user subroutine in FORTRAN in the Abaqus FE code, we have recently proposed in Pantalé \eal \cite{Pantale-2021} an alternative approach based on the ability of Artificial Neural Networks (ANNs) to behave as universal approximators as reported by Minsky \eal \cite{Minsky-1969} and Hornik \eal \cite{Hornik-1989}.
In fact, Artificial Neural Networks can solve problems that are difficult to conceptualize using traditional computational methods.
Unlike a classical approach based on a regression method, an ANN does not need to know the mathematical form of the model it seeks to reproduce, hence we do not need anymore to postulate the mathematical form of the constitutive equation to use it in a FE simulation using this kind of approach.

@@

Since, as reported in Figure \ref{fig:Convergence-ANN}, the 3-7-4-1 model seems to have converged after the training phase, we are going to compare it with the 'accurate' model, the 3-15-7-1 model.
From a more physical point of view, Figures \ref{fig:CompExpANN-9-4} and \ref{fig:CompExpANN-15-7} show the correlation between the data predicted by the neural network and the experimental data for the 3-7-4-1 and 3-15-7-1 networks respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/CompExpANN-3-7-4-1}
\caption{Comparison of the flow stress $\sigma^y$ predicted by the 3-7-4-1 ANN and the experimental data for the GCr15.}
\label{fig:CompExpANN-9-4}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/CompExpANN-3-15-7-1}
\caption{Comparison of the flow stress $\sigma^y$ predicted by the 3-15-7-1 ANN and the experimental data for the GCr15.}
\label{fig:CompExpANN-15-7}
\end{figure}
Analysis of Figures \ref{fig:CompExpANN-9-4} and \ref{fig:CompExpANN-15-7} shows a very good correlation between the ANN results and the experimental results, which is reflected by the very low values of the $\MARE$ and $\RMSE$ coefficients reported in Table \ref{tab:ErrorANN}.
As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
This is why this type of coefficient is not used in this work for comparing the different models.

>>>>

As we have seen in the previous paragraph, the choice of the flow law to use is generally guided mainly by the list of flow laws available in the Finite Element code used, and very often this choice is made at the expense of the quality of the model.
For example, Zhou \eal \cite{Zhou-2020}, proposed the identification of the flow law of a GCr15 alloy for a continuous casting bloom with heavy reduction application as introduced by Ji \eal \cite{Ji-2018} who have performed compression tests on this material.
In their study, Ji \eal \cite{Ji-2018} performed compression tests on GCr15 cylinders in a temperature range of $750~\celsius$ to $1300~\celsius$ in $50~\celsius$ steps, strain rates of $0.001~\ps$,  $0.01~\ps$ and $0.1~\ps$ and strains up-to $0.7$.
The results of these compression tests, plotted in Figure \ref{fig:Zhou-OriginalData}, show a decrease in flow stress $\sigma^y$ with respect to an increase of the temperature $T$ and a increase of $\sigma^y$ with respect to an increase of the strain rate $\mdot\varepsilon$, as in most metallic materials.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/Zhou-OriginalData}
\caption{Original data extracted from the publication of Ji \eal \cite{Ji-2018}.}
\label{fig:Zhou-OriginalData}
\end{figure}
The evolution of the flow stress as a function of the plastic deformation shows the presence of a dynamic recrystallization (DRX) phenomenon within the material.
This phenomenon is an additional non-linearity of this type of material compared to other materials, mainly due to high temperatures and low strain rates, which should be taken into account when describing the material behavior.
As stated in the publication of Zhou \eal \cite{Zhou-2020}, depending on the flow model used: Johnson-Cook, Modified Zerilli-Armstrong, Arrhenius or new Modified Johnson-Cook, the fidelity of taking into account the real behavior varies widely with the complexity of the flow model which includes between $5$ parameters for the Johnson-Cook model, and $16$ parameters for the Arrhenius model.
Thus, and for the input data provides by Ji \eal \cite{Ji-2018}, the two most common models: Johnson-Cook and Zerilli-Armstrong do not correctly describe the material behavior.
Only the modified Johnson-Cook and Arrhenius models are able to describe correctly the behavior of the material during the compression process.
Unfortunately, and this is not part of their study, if these last two models are satisfactory from a theoretical point of view, from a practical point of view for the user of a FE code such as Abaqus, it will be necessary to carry out a numerical implementation in a FORTRAN 77 VUMAT subroutine of the modified Johnson-Cook flow law or the Arrhenius law as carried out by few authors \cite{Liang-2022, Gao-2007-FRT, Ming-2018} in order to be able to use these laws for numerical simulation.
This requires a certain expertise in the development and implementation of flow laws, which is not available to all users of the Abaqus FE code.

From this observation, and from the necessity to select a flow law for a given type of material, then to identify the parameters of this flow law according to experimental tests, and finally to implement this flow law in the form of a user subroutine in FORTRAN in the Abaqus FE code, we have recently proposed in Pantalé \eal \cite{Pantale-2021} an alternative approach based on the ability of Artificial Neural Networks (ANNs) to behave as universal approximators as reported by Minsky \eal \cite{Minsky-1969} and Hornik \eal \cite{Hornik-1989}.
In fact, Artificial Neural Networks can solve problems that are difficult to conceptualize using traditional computational methods.
Unlike a classical approach based on a regression method, an ANN does not need to know the mathematical form of the model it seeks to reproduce, hence we do not need anymore to postulate the mathematical form of the constitutive equation to use it in a FE simulation using this kind of approach.
Using a Neural Network instead of an analytical constitutive law can lead to a bias related to the validity of the answers according to the domain of use and the learning domain. 
Thus, if ANNs are efficient for the interpolation of results inside the learning domain, their behavior outside of it is not controlled. 
Therefore, if the input values are far from those provided during the training, the outputs can be far from the physical reality of the process. 
It is, of course, the same for analytical laws when modeling non-linear behavior, but if the choice of the model has been made properly, based on physical considerations, they will provide results closer to reality than the ANN model. 
Therefore, care should be taken when using ANN-based flow laws and the validity of the model input data should always be verified.

@@

Since, as reported in Figure \ref{fig:Convergence-ANN}, the 3-7-4-1 model seems to have converged after the training phase, we are going to compare it with the 'accurate' model, the 3-15-7-1 model.
From a more physical point of view, Figures \ref{fig:CompExpANN-9-4} and \ref{fig:CompExpANN-15-7} show the correlation between the data predicted by the neural network and the experimental data for the 3-7-4-1 and 3-15-7-1 networks respectively.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/CompExpANN-3-7-4-1}
\caption{Comparison of the flow stress $\sigma^y$ predicted by the 3-7-4-1 ANN (continuous line) and the experimental data for the GCr15 (square markers).}
\label{fig:CompExpANN-9-4}
\end{figure}
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/CompExpANN-3-15-7-1}
\caption{Comparison of the flow stress $\sigma^y$ predicted by the 3-15-7-1 ANN (continuous line) and the experimental data for the GCr15 (square markers).}
\label{fig:CompExpANN-15-7}
\end{figure}
Analysis of Figures \ref{fig:CompExpANN-9-4} and \ref{fig:CompExpANN-15-7} shows a very good correlation between the ANN results and the experimental results, which is reflected by the very low values of the $\MARE$ and $\RMSE$ coefficients reported in Table \ref{tab:ErrorANN}.
As reported by Phaniraj \cite{Phaniraj-2003}, the correlation coefficient ($\R$) is generally not a good measure in our case of study because it only shows the correlation of the model with respect to the data and not its accuracy, which is a determining factor in the qualification of a model.
This is why this type of coefficient is not used in this work for comparing the different models.
